### 2021-12-10 manuscript.tex
Fix more typos and clumsy phrasing

They rounded a corner, and Bradley ushered Sascha into a dim room.  There were two tables pushed agaist a wall, a gray coatrack in the corner, and the wall appeared to be glowing.  Once his eyes adjusted, Jesse realized that he was looking into a one-way mirror, and on the other side was a bright interrogation room.  Inside the room there were two simple chairs that reminded him of the cheap variety that his elementary school had used.  He discovered, with relief, that the chairs on the near side of the mirror were cushioned and comfortable.  There were four chairs in total, two at each of the tables.  A pitcher of water and six plain-looking glasses sat on the table to Jesse's left.

@@

``In Hungary, politicians do not become wealthy when they are in public office.  They cannot.  This is true in many European countries.  One does not need to be rich to become elected, and one cannot become rich after election.  Business does not corrupt politics with too much money.  If someone is elected, he wants to serve Hungary.  One of your writers said that nobody who wants to be president should become president.''

@@

Jesse considered him for a long moment.  It was starting to sink in that his evening plans were not going to come to fruition.  After the interrogation, he was going to visit a restaurant where he had eaten when he first moved to the city.  It was a quiet place that served bar food and was in a neighborhood off the beaten path that none of his friends or colleagues had heard of.  That would have to wait.  Sascha would have a plan, and Jesse knew that his only play was to trust the former marine's prodigious judgment.  \emph{He's better half asleep than I've ever been}.

@@

``I know just the spot.  And there's a restaurant with great take-away about 100 yards away.''

@@

``Normally I would be taking one.  The officer who dropped me off mentioned that this was a very active neighborhoods.  Apparently there are 5K runs five times per year during the warmer months.  It's my kind of place when I'm not being stalked.''

@@

Sascha barely had time to wonder about the situation before he heard more heavy footsteps on the stairway.  A look of fear come over Beata's face, and she scurried across the room to take up a position next to her remaining comrade.  They both aimed their guns at the door.  Jesse and Sascha, sensing that more violence was on the way, crawled out of the room.

@@

It was still early enough that no one was at work, draining Jesse's hope that he could communicate his distress to someone he knew.  He led the entourage through the entrance to the building and walked toward the north elevator.  They were two floors above the floor that housed the vault.  Jesse punched the button labeled \texttt{B2} and waited for the doors to close.  He wished that Sascha were here.  There was much more space available to them now that they were out of the apartment, and Jesse knew that Sascha would be able to manufacture an escape.  \emph{Jenna probably knows just how capable he is, too}, he thought.  \emph{I'm on my own this time}.  He still had no idea what he would do when they got to the door of the vault.  He had no key, no passcode, and no intention of opening the door.

@@

Forth punched the \texttt{UNLOCK} button and looked sidelong at Jesse.  ``It's time to face the music, Mr. Winter.''  He pulled the large handle, and the heavy door yawned open again.  The red-faced gunmen and Jenna came out, glaring at Jesse.  Jenne stepped forward and shoved him.  ``Did you think that little prank was cute?'' she said, hardly interested in an answer.  ``I'll show you cute.''  She pulled her handgun from its holster and grabbed Jesse by his shirt, pushing him against the wall.  She pushed the gun into his cheek, and he could feel the cold steel compressing his nasal cavity.  He closed his eyes.

@@

Jesse was stunned.  He had hoped that the Forth would see prison time.  Based on what had happened in the previous 48 hours, tying Forth to Ingo and establishing that they were cooperating in organized crime would be easy.  Jesse had never met the head of the NYPD, though, and couldn't believe that this dust-up was going to have such broad reach.  Talk about bringing down an elephant.

>>>>

They rounded a corner, and Bradley ushered Jesse into a dim room.  There were two tables pushed agaist a wall, a gray coatrack in the corner, and the wall appeared to be glowing.  Once his eyes adjusted, Jesse realized that he was looking into a one-way mirror, and on the other side was a bright interrogation room.  Inside the room there were two simple chairs that reminded him of the cheap variety that his elementary school had used.  He discovered, with relief, that the chairs on the near side of the mirror were cushioned and comfortable.  There were four chairs in total, two at each of the tables.  A pitcher of water and six plain-looking glasses sat on the table to Jesse's left.

@@

``In Hungary, politicians do not become wealthy when they are in public office.  They cannot.  This is true in many European countries.  One does not need to be rich to become elected, and one cannot become rich after election.  Business does not corrupt politics with too much money.  If someone is elected, he wants to serve Hungary.  Someone said that nobody who wants to be president should become president.''

@@

Jesse considered him for a long moment.  It was starting to sink in that his evening plans were not going to come to fruition.  After the interrogation, he was going to visit a restaurant where he had eaten when he first moved to the city.  It was a quiet place that served bar food and was in a neighborhood off the beaten path that none of his friends or colleagues had heard of.  That would have to wait.  Sascha would have a plan, and Jesse knew that his only play was to trust the former Marine's prodigious judgment.  \emph{He's better half asleep than I've ever been}.

@@

``I know just the spot.  And there's a great takeout joint about 100 yards away.''

@@

``Normally I would be taking one.  The officer who dropped me off mentioned that this was a very active neighborhood.  Apparently there are 5K runs a few times a year during the warmer months.  It's my kind of place when I'm not being stalked.''

@@

Sascha barely had time to wonder about the situation before he heard more heavy footsteps on the stairs.  A look of fear came over Beata's face, and she scurried across the room to take up a position next to her remaining comrade.  They both aimed their guns at the door.  Jesse and Sascha, sensing that more violence was on the way, crawled out of the room.

@@

It was still early enough that no one was at work, draining Jesse's hope that he could communicate his distress to someone he knew.  He led the entourage through the entrance to the building and walked toward the north elevator.  They were two floors above the one that housed the vault.  Jesse punched the button labeled \texttt{B2} and waited for the doors to close.  He wished that Sascha were here.  There was much more space available to them now that they were out of the apartment, and Jesse knew that Sascha would be able to manufacture an escape.  \emph{Jenna probably knows just how capable he is, too}, he thought.  \emph{I'm on my own this time}.  He still had no idea what he would do when they got to the door of the vault.  He had no key, no passcode, and no intention of opening the door.

@@

Forth punched the \texttt{UNLOCK} button and looked sidelong at Jesse.  ``It's time to face the music, Mr. Winter.''  He pulled the large handle, and the heavy door yawned open again.  The red-faced gunmen and Jenna came out, glaring at Jesse.  Jenna stepped forward and shoved him.  ``Did you think that little prank was cute?'' she said, hardly interested in an answer.  ``I'll show you cute.''  She pulled her handgun from its holster and grabbed Jesse by his shirt, pushing him against the wall.  She pushed the gun into his cheek, and he could feel the cold steel compressing his nasal cavity.  He closed his eyes.

@@

Jesse was stunned.  He had hoped that Forth would see prison time.  Based on what had happened in the previous 48 hours, tying Forth to Ingo and establishing that they were cooperating in organized crime would be easy.  Jesse had never met the head of the NYPD, though, and couldn't believe that this dust-up was going to have such broad reach.  Talk about bringing down an elephant.
